Dirac neutrino mass generation from Majorana messenger

### 2019-09-23 draft.tex
Updates from Overleaf

The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}, where it can be observed that for small ratios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
% The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound at $2\sigma$ (solid gray line) demands that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV (these bounds become slightly weaker once the Planck+BAO+$H_0$ combination~\cite{Aghanim:2018eyx} is considered, but in such a case the BBN bound from the primordial abundances of light elements would rule~\cite{Pitrou:2018cgg}). 
%in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
In other words, bearing in mind that $M_{Z'}/g'=3v_S/2$ we have that the energy scale of the $\operatorname{U}(1)_{X}$ symmetry breaking must be at least $\sim26$ TeV.      
On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}. The same constraint would apply to all gauged and anomaly free  $\operatorname{U}(1)_X$ extensions of the SM with Dirac neutrino masses, where light right handed neutrinos are associated  to the solution $(-4,-4,+5)$~\cite{Ma:2014qra,Ma:2015mjd,Ma:2015raa,Bonilla:2018ynb,Calle:2018ovc,Bonilla:2019hfb}

>>>>

The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}, where it can be observed that for small ratios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
% The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound at $2\sigma$ (solid gray line) demands that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV (these bounds become slightly weaker once the Planck+BAO+$H_0$ combination~\cite{Aghanim:2018eyx} is considered, but in such a case the BBN bound from the primordial abundances of light elements would rule~\cite{Pitrou:2018cgg}). 
%in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
In other words, bearing in mind that $M_{Z'}/g'=3v_S/2$ we have that the energy scale of the $\operatorname{U}(1)_{X}$ symmetry breaking must be at least $\sim26$ TeV.      
On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}. The same constraint would apply to all gauged and anomaly free  $\operatorname{U}(1)_X$ extensions of the SM with Dirac neutrino masses, where light right handed neutrinos are associated  to the solution $(-4,-4,+5)$~\cite{Ma:2014qra,Ma:2015mjd,Ma:2015raa,Bonilla:2018ynb,Calle:2018ovc,Bonilla:2019hfb}.
